---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# disco

This package provides 9 discrete color palettes developed by Paul Tol at <https://personal.sron.nl/~pault/> for qualitative, diverging, and sequential data. Colors within each palette are designed to match well together and be readable by all audiences, including color-blind readers.

## Installation

`disco` can be installed directly from GitHub:

```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("nsgrantham/disco")
```

## Palettes

The `disco` API is similar to other color palette packages like [`viridis`](https://github.com/sjmgarnier/viridis) and [`scico`](https://github.com/thomasp85/scico).

View all 9 color palettes with `disco_palettes_show()` 

```{r show}
library(disco)

disco_palette_show()
```

The following table summarizes the 9 color palettes. For more information, consult Paul Tol's Notes <https://personal.sron.nl/~pault/>.

| Palette | n | Data type | Description |
|--------------|------------------|-----------|-------------|
|bright|7|Qualitative|Good for lines and their labels.|
|vibrant|7|Qualitative|Built around the signature orange #FF7043 of the data visualization framework TensorBoard.|
|muted|10|Qualitative|Good for lines and maps.|
|light|9|Qualitative|Good for filled cells and backgrounds because it keeps black text readable.|
|sunset|11|Diverging|This is related to the ColorBrewer RdYlBu scheme, but with darker central colours and made more symmetric.|
|daybreak|9|Diverging|This is the reversed ColorBrewer RdBu scheme.|
|midnight|9|Diverging|This is the ColorBrewer PRGn scheme, with green #A6DBA0 shifted to #ACD39E to make it print-friendly.|
|eclipse|9|Sequential|This is the ColorBrewer YlOrBr scheme, with orange #FE9929 shifted to #FB9A29 to make it print-friendly.|
|rainbow|23|Sequential|This should not be used on a continuous scale, but on a discrete scale it offers up to 23 colors and remains relatively color-blind safe.|

Select a palette by name:

```{r hex}
disco(palette = "sunset")
```

Scales are provided for `ggplot2`:

```{r ggplot2, warn=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(gapminder)

ggplot(filter(gapminder, year == 2007), 
       aes(gdpPercap, lifeExp, size = pop, color = continent)) +
  geom_point() +
  scale_color_disco(palette = "vibrant")
```

Happy plotting!

## References

<https://www.colorbrewer2.org> by Cynthia A. Brewer, Geography, Pennsylvania State University  
<https://personal.sron.nl/~pault/> by Paul Tol, Netherlands Institute for Space Research (SRON) 
